A simulation framework for exploring spatio-temporal dynamics in mixed fisheries

### 2018-01-30 write_up/mixfishsim_ecolmod.tex
Updates to manuscript

\begin{abstract}
[Guidance: A concise and factual abstract is required. The abstract should
state briefly the purpose of the research, the principal results and major
conclusions. An abstract is often pnresented separately from the article, so it
must be able to stand alone. For this reason, References should be avoided, but
if essential, then cite the author(s) and year(s). Also, non-standard or
uncommon abbreviations should be avoided, but if essential they must be defined
at their first mention in the abstract itself.  Graphical abstract: Although a
graphical abstract is optional, its use is encouraged as it draws more
attention to the online article. The graphical abstract should summarize the
contents of the article in a concise, pictorial form designed to capture the
attention of a wide readership. Graphical abstracts should be submitted as a
separate file in the online submission system. Image size: Please provide an
image with a minimum of 531 X 1328 pixels (h X w) or proportionally more. The
image should be readable at a size of 5 x 13 cm using a regular screen
resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or MS Office
files.]
\end{abstract}

\begin{keyword}
Some\sep keywords \sep here. Max 6, American "spelling" 
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

[Guidance:: State the objectives of the work and provide an adequate
background, avoiding a detailed literature survey or a summary of the results.]
\\

@@

[Guidance: Provide sufficient details to allow the work to be reproduced by an
independent researcher. Methods that are already published should be
summarized, and indicated by a reference.  If quoting directly from a
previously published method, use quotation marks and also cite the source. Any
modifications to existing methods should also be described.] \\

@@

[Guidance: A Theory section should extend, not repeat, the background to the
article already dealt with in the Introduction and lay the foundation for
further work.  In contrast, a Calculation section represents a practical
development from a theoretical basis.] \\

@@

@@

@@

[Guidance: Results should be clear and concise.]

@@

[Guidance: This should explore the significance of the results of the work, not
repeat them. A combined Results and Discussion section is often appropriate.
Avoid extensive citations and discussion of published literature.]

@@

[Guidance: The main conclusions of the study may be presented in a short Conclusions
section, which may stand alone or form a subsection of a Discussion or Results
and Discussion section.]

@@

[Guidance: If there is more than one appendix, they should be identified as A, B, etc.
Formulae and equations in appendices should be given separate numbering: Eq.
(A.1), Eq. (A.2), etc.; in a subsequent appendix, Eq. (B.1) and so on.
Similarly for tables and figures: Table A.1; Fig. A.1, etc.]

>>>>

\begin{abstract}
\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
should state briefly the purpose of the research, the principal results and
major conclusions. An abstract is often pnresented separately from the article,
so it must be able to stand alone. For this reason, References should be
avoided, but if essential, then cite the author(s) and year(s). Also,
non-standard or uncommon abbreviations should be avoided, but if essential they
must be defined at their first mention in the abstract itself.  Graphical
abstract: Although a graphical abstract is optional, its use is encouraged as
it draws more attention to the online article. The graphical abstract should
summarize the contents of the article in a concise, pictorial form designed to
capture the attention of a wide readership. Graphical abstracts should be
submitted as a separate file in the online submission system. Image size:
Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
proportionally more. The image should be readable at a size of 5 x 13 cm using
a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
MS Office files.] \\}

Fishing exploits spatio-temporally hetergenous fish populations without fully
selective gear which can result in unintended, unwanted catch of low quota or
protected species. Reducing these unwanted catches is crucial for biological
and economic sustainability of 'mixed fisheries'. \\

Understanding of spatio-temporal fishery dynamics is limited by a lack of full
understanding of population distribution and how fishers interact with the
different populations. We develop a spatio-temporal simulation model that
incorporate i) delay-difference population dynamics, ii) population movement
dynamics using Gaussian Random Fields, iii) fishery dynamics for multiple fleet
characteristics based on a correlated random walk and learned behaviour. \\

Using our model we simulation 20 years of exploitation of the fish populations
and use the results from the fishing model to draw inference on the underlying
population structures.  We compare this inference to i) a simulated fixed-site
sampling design commonly used for fisheries monitoring purposes, ii) the
underlying population structures input to the simulation.\\

We find that... \\

\end{abstract}

\begin{keyword}
Some\sep keywords \sep here. Max 6 
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

\textcolor{gray}{[Guidance:: State the objectives of the work and provide an adequate
background, avoiding a detailed literature survey or a summary of the results.]
\\}

@@

\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
reproduced by an independent researcher. Methods that are already published
should be summarized, and indicated by a reference.  If quoting directly from a
previously published method, use quotation marks and also cite the source. Any
modifications to existing methods should also be described.] \\ }

@@

\textcolor{gray}{[Guidance: A Theory section should extend, not repeat, 
the background to the article already dealt with in the Introduction and lay
the foundation for further work.  In contrast, a Calculation section represents
a practical development from a theoretical basis.] \\}

@@

The fleets were parameterised to reflect five different characteristics based
on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
ensures that different fleets have different spatial dynamics, preferentially
targeted different fish populations. The stochasticity in the random walk
process ensures that different vessels within a fleet have slightly different
spatial distributions based on individual experience. \\

Each fleet was set so that, after the first year, fishing locations were chosen
based on experience built up in the same month from previous years and from
past trip fishing success. 'Success' in this context was defined as the
locations where the top 75 \% of revenue from previous trips was found. \\

@@

\subsection{Survey settings}

The survey simulation was set up with follow a fixed gridded station design
with 49 stations fished each year, starting on day 92 with same catchability
parameters for all populations (Q = 1). \\

@@

\textcolor{gray}{[Guidance: Results should be clear and concise.]}

@@

\textcolor{gray}{[Guidance: This should explore the significance of the results 
of the work, not repeat them. A combined Results and Discussion section is
often appropriate.  Avoid extensive citations and discussion of published
literature.]}

@@

textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
in a short Conclusions section, which may stand alone or form a subsection of a
Discussion or Results and Discussion section.]}

@@

\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
be identified as A, B, etc.  Formulae and equations in appendices should be
given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
Fig. A.1, etc.]}
